The Astropy Project

### 2017-10-05 main.tex
Converted comment questions to inlinecomments

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy{} project is the concept of “Affiliated
Packages”. An affiliated package is an astronomy-related Python package that
is not part of the \astropypkg{} core package, but has requested to be
included as part of the astropy project’s community. These packages support
the goals and vision of \astropy{} of improving code reuse,
interoperability, and embracing good coding practices such as testing and
thorough documentation. \astropypkg{} currently supports both versions of
Python 2.7+ and Python 3.x, affiliated packages are strongly encouraged to
support at least Python 3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. In general we hope that
becoming an affiliated package is seen as a good way for new and existing
packages to gain exposure.
%
% TODO: write about the process of becoming affiliated, and project packages
%
\subsection{Mixin}

@@

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
%\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
% - reference APE2 for versioning and APE10 for dropping python2 support
% - shall we maybe refer to the release calendar, too?
% - should we mention that v3.0 is the exception to the version numbering
%   scheme we use by not being 2.1?
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. \astropypkg\ has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features. The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg\ reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
% - should we use links to the appropriate github repo?
% - should we describe astropy-helpers even though it's future is unsure?
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy\ provides a template package that any \python\ package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\texttt{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy\ ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R

@@

\section{Learning Astropy}
\label{sec:learning}
% Kelle, Adrian
% - would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?

>>>>

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy{} project is the concept of “Affiliated
Packages”. An affiliated package is an astronomy-related \python{} package that
is not part of the \astropypkg{} core package, but has requested to be
included as part of the astropy project’s community. These packages support
the goals and vision of \astropy{} of improving code reuse,
interoperability, and embracing good coding practices such as testing and
thorough documentation. \astropypkg{} currently supports both versions of
\python\ 2.7+ and \python\ 3.4, affiliated packages are strongly encouraged to
support at least \python\ 3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. In general we hope that
becoming an affiliated package is seen as a good way for new and existing
packages to gain exposure.
%
% TODO: write about the process of becoming affiliated, and project packages
%
\subsection{Mixin}

@@

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
%
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. \astropypkg\ has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features. The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg\ reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
\inlinecomment{BMS}{should we use links to the appropriate github repo?}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy\
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
\par \astropy\ provides a template package that any \python\ package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\texttt{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy\ ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R

@@

\section{Learning Astropy}
\label{sec:learning}
% Kelle, Adrian
\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}
